Hijacking Simulators with Universal Probabilistic Programming

### 2019-07-25 paper/learning/notes.tex
updated

One recent technique for density estimation, in the amortized inference setting,
is normalising flows combined with variation inference~\cite{rezende2015variational}.
Flow-based methods work by leveraging a simple property of differential geometry applied 
to random variables. 
That being the change of variables.
Let $z \sim r(z)$ where $r(z)$ represents the posterior defined by the rejection
sampling loop, and define $\pi$ to be a smooth and invertible function.
When $\pi$ acts $z$ we transform the random variable from one domain, to another. 
Thus, if $z\prime = \pi(z)$ then we can construct the density of  
the probability density of the new random variable $z\prime$ under the flow initiated by $\pi$: 
\begin{equation}
r(z\prime) = r(\pi^{-1}(z\prime)) \left|\det \frac{\partial \pi^{-1}}{\partial z'}\right| = r(\pi^{-1}(z\prime)) \left|\det \frac{\partial \pi}{\partial z\prime}\right|^{-1} 
\end{equation}
However, since 
where the $y$'s are generated from the rejection sampling loops.

\begin{itemize}
  \item Do we need to know the base distribution that the RS block is sampling from? i.e there maybe be multiple $\pi(\epsilon)$ in each 
  RS block. 
  \item Is it right to say here that $y$ is the output of the RS block, we do not know $f$ here. 
  \item We need to learn $f(.)$
\end{itemize}

>>>>

One recent technique for density estimation, in the amortized inference setting,
is normalising flows combined with variation inference~\cite{rezende2015variational}.
Flow-based methods work by leveraging a simple property of differential geometry applied 
to random variables. 
That being the change of variables.
Let $z \sim r(z)$ where $r(z)$ represents the posterior defined by the rejection
sampling loop, and define $\pi$ to be a smooth and invertible function.
When $\pi$ acts $z$ we transform the random variable from one domain, to another. 
Thus, if $z\prime = \pi(z)$ then we can construct the density of  
the probability density of the new random variable $z\prime$ under the flow initiated by $\pi$: 
\begin{equation}
r(z\prime) = r(\pi^{-1}(z\prime)) \left|\det \frac{\partial \pi^{-1}}{\partial z'}\right| = r(\pi^{-1}(z\prime)) \left|\det \frac{\partial \pi}{\partial z\prime}\right|^{-1} 
\end{equation}

\begin{itemize}
  \item Do we need to know the base distribution that the RS block is sampling from? i.e there maybe be multiple $r(z)$ in each 
  RS block. 
  \item Is it right to say here that $z\prime$ is the output of the RS block, we do not know $\pi$ here, or is $r(z)$ the raw sample $f_{a_i}$ and $\pi$ the distribution specified by the rejection sampling loop? 
  \item We need to learn $\pi(.)$
\end{itemize}
